---
title: "Assignment - HTML process"
author: "Abduvosid Malikov"
date: "23 November"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

## Introduction

This is the Assignment for `Web Scraping with R` course. As a source,  [vox](https://www.vox.com/search?page=1&q=Biden) news website was scraped. 

## First function

This function accepts url as an argument. Then it downloads information from that passed url to dataframe 



## Your Familiar Tools

Feel free to use the `knitr` infrastructure with dozens of tunable options in
your document.

```{r fig.width=6, fig.height=6, fig.align='center'}
set.seed(123)
n <- 1000
x1  <- matrix(rnorm(n), ncol = 2)
x2  <- matrix(rnorm(n, mean = 3, sd = 1.5), ncol = 2)
x   <- rbind(x1, x2)
head(x)
smoothScatter(x, xlab = "x1", ylab = "x2")
```

You can include code snippets of languages other than R, but note that
the block header has no curly brackets around the language name.

```cpp
// [[Rcpp::export]]
NumericVector timesTwo(NumericVector x) {
    return x * 2;
}
```

You can also write math expressions, e.g. $Y = X\beta + \epsilon$,
footnotes^[search term used: 'Biden'.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(iris, 10))
```

